\documentclass{report}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{graphicx}
\usepackage{float}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{datetime}
\usepackage{mathtools}

% Config taken from http://tex.stackexchange.com/a/68092
\lstset{language=C++,
  basicstyle=\ttfamily,
  keywordstyle=\color{blue}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  commentstyle=\color{green}\ttfamily,
  morecomment=[l][\color{magenta}]{\#}
}

\title{\textsc{libdepixelize algorithmic documentation}}
\author{Vinícius dos Santos Oliveira}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\pagebreak

\chapter{Preface}

This document is a project to centralize the knowledge required to implement the
\href{http://research.microsoft.com/en-us/um/people/kopf/pixelart/}{Kopf-Lischinski}
vectorizer algorithm. It was created as part of the
\href{http://www.google-melange.com/gsoc/project/google/gsoc2013/vinipsmaker/48002}{GSoC
2013's libdepixelize project}.

Another goal of this document is to ease the comprehension of
\href{https://launchpad.net/libdepixelize}{libdepixelize}'s source code. That
said, documentation of techniques used in libdepixelize will be favored over
other techniques. Keep in mind that this document is \textbf{not}
documentation for the libdepixelize source code and may be useful independently
from it, but libdepixelize maintainers will greatly benefit from this document.

The initial content of this document was adapted from posts published during the
development of libdepixelize on
\href{http://vinipsmaker.wordpress.com/category/computacao/gsoc2013-inkscape/}{Vinipsmaker
labs}, the original libdepixelize author's blog. The adaptation includes:

\begin{itemize}
\item Replacing several of the media assets by higher quality files.
\item Restructure the order of the posts to make the documentation more didatic.
\item Review the text and update it to refer to the libdepixelize's current
  techniques.
\end{itemize}

All images in this document, unless explicitly stated otherwise, were created
using Inkscape and its awesome alignment tools.

This document is dedicated to the Inkscape community.

\chapter{Introduction}

Playing video games is a part of the life of several people already and in the
beginning of this new kind of entertainment, a lot of love was invested in the
creation of beautiful images where the pixels were carefully put together.

Time went by on and the age of ``pixel art'' was momentarily\ldots{}
forgotten\ldots{} replaced by more demanding art after more and more powerful
devices started to appear.

Some people were never able to forget pixel art and continued to play ancient
games just for the sake of nostalgia. The emulation community was born with the
intent to revive the classic moments and it produced some awesome tools over the
time.

In 2011, a new technology excited the emulation forums. This new technology was
an algorithm created by Johannes Kopf and Dani Lischinski that could create
resolution independent vector graphics representations out of pixel art images.

And then you came here and have this document that will surely be your lovable
guide in the challenging quest of implementing the wonderful Kopf-Lischinski
algorithm. What are you waiting for? Go on and proceed to the next page.

\section{Requirements}

Understanding Bézier curves is a must for this document and if the reader is not
very familiar with these curves, \emph{vinipsmaker} suggests you to read the
excellent \href{http://pomax.github.io/bezierinfo/}{Pomax's \emph{A Primer on
Bezier Curves}}. If you think Pomax's text is too advanced, you can start with
\href{http://jeremykun.com/2013/05/11/bezier-curves-and-picasso/}{Math $\cap$
Programming} blog.

\chapter{Splines extraction on Kopf-Lischinski algorithm}

Well, one of the phases in the algorithm is splines extraction. This phase
creates a pipeline (output from one step is the input of the next) like the
following:

\begin{enumerate}
\item It takes the color similarity graph
\item It generates a generalized Voronoi diagram
\item It groups the voronoi cells to identify visible edges
\item It generates the splines
\end{enumerate}

\hyperref[blogpart0]{Part 0} explains a fast method to compute the Voronoi
diagram exploring special properties of the input graph.
\hyperref[blogpart1]{Part 1} explains a fast method to add polygons together
exploring special properties of the generated Voronoi diagram and the data
layout used in libdepixelize. \hyperref[blogpart2]{Part 2} explains how to
generate the Bézier curves. \hyperref[tjunction]{T-junction} section discusses
how to handle T-junction nodes.

The names of the sections are based on the titles of the original posts where
they came from.

\section{Part 0}
\label{blogpart0}
\input{blog/part0.tex}

\section{Part 1}
\label{blogpart1}
\input{blog/part1.tex}

\section{Part 2}
\label{blogpart2}
\input{blog/part2.tex}

\section{T-junctions}
\label{tjunction}
\input{src/tjunction.tex}

\chapter{The \emph{extra color information} patch}
\label{extracolor}
\input{src/extracolor.tex}

\chapter{Optimizing the B-Splines}
\label{optimizing}
\input{src/optimizing.tex}

\appendix
\chapter{Complete smoothness code (without the extra color
  patch)}
\label{smoothness_code_appendix}
\input{src/smoothness_code_appendix.tex}

\end{document}
